
\documentclass[cards,frame]{flashcards}
\usepackage[utf8]{inputenc}
\cardfrontheadstyle[\ttfamily]{left}
\cardfrontfootstyle[\small\itshape]{left}
\cardfrontstyle{headings}
\newcommand\black{{\huge Black}\par\bigskip Cards\\ Against\\ IT\par\bigskip{\huge Black}}
\newcommand\white{{\huge White}\par\bigskip Cards\\ Against\\ IT\par\bigskip{\huge White}}
\begin{document}
\cardfrontfoot{CVAdmin}

    \begin{flashcard}
    [1 $Black$ ]
    {\_\_\_\_\_\_ can sink the directory faster.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {\_\_\_\_\_\_ will unstick an unkillable rm.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Always \_\_\_\_\_\_\_ when installing.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Don't \_\_\_\_\_\_\_ the gateway.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {There's a \_\_\_\_\_\_ in the emergency toolbox.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {In case of emergency someone help with \_\_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {All persons in the datacenter must have a \_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {In case of a fire, grab \_\_\_\_\_\_ first.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {New users should try \_\_\_\_\_\_\_\_ first.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {\_\_\_\_\_\_\_\_\_\_\_ fixes everything.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Our contributing policy is \_\_\_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Our new platform is \_\_\_\_\_\_\_ enabled.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Remember you were hired to \_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {\_\_\_\_\_\_\_\_ is the first stage of our rollout.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Level One personell are identified by \_\_\_\_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {\_\_\_\_\_\_\_.sexy}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {RMS approves of \_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {If everyone is dead get \_\_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Always ask \_\_\_\_\_\_\_\_\_ first.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Do \_\_\_\_\_ before you push.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {We once killed the network with \_\_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {FreeBSD is only good for \_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Check the whiteboard for \_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Never touch \_\_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Don't ask about \_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {Jump start a PC with \_\_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $Black$ ]
    {The secret to IT is \_\_\_\_\_\_\_\_\_.}
    \black
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A realm fault}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A 250 foot ethernet cable}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {The Firewall}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {An OpenBSD Install Disk}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A FreeBSD Install Disk}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {UBUNTU!!!!!!!}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A PL/SQL Manual}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A ream of paper}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A cups error}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {Halt Catch-Fire}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A projector remote}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A hapless user}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {Microsoft Office}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {WPS Office}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {Lemonaide}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {An overloaded jump host}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A dell monitor cable}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {LDAP}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {An OID Arc}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {Changing my uid}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {Systemd}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {Lennart Poeterring}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {The Free Software Foundation}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {RMS}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {The Free Desktop Movement}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A RedHat engineer}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {Windows NT}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A windows license}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A giant stuffed tux.}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {Freezy Pops}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {IRC}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {Linus}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A datacenter extension cord}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {A UPS}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {600 feet of fiber behind the server rack}
    \white
    \end{flashcard}
    
    \begin{flashcard}
    [1 $White$ ]
    {The BofH}
    \white
    \end{flashcard}
    
\end{document}

